\bf Supervised Tensor Decomposition with Side-information on Multiple Modes

### 2020-09-02 tensor_regress/jasa-latexsource/tensor-jasa.tex
update

\if1\blind
{
  \title{\bf Supervised Tensor Decomposition with Covariates on Multiple Modes}
  \author{Jiaxin Hu, Zhuoyan Xu, and Miaoyan Wang\\
    Department of Statistics, University of Wisconsin-Madison}
  \maketitle
} \fi

@@

\bigskip
\begin{abstract}
We consider the problem of supervised tensor decomposition given covariates on multiple modes. Such data problems arise frequently in applications such as neuroimaging, network analysis, and spatial-temporal modeling. We propose a new family of tensor response regression models that incorporate covariates, and establish the theoretical accuracy guarantees. Unlike earlier methods, our estimation allows high-dimensionality in both the tensor response and the covariate matrices on multiple modes. An efficient alternating updating algorithm is further developed. Our proposal handles a broad range of data types, including continuous, count, and binary observations. Through simulation and applications to two real datasets, we demonstrate the outperformance of our approach over the state-of-art.
\end{abstract}

>>>>

\if1\blind
{
  \title{\bf Supervised Tensor Decomposition with Side-information on Multiple Modes}
  \author{Jiaxin Hu, Zhuoyan Xu, and Miaoyan Wang\\
    Department of Statistics, University of Wisconsin-Madison}
  \maketitle
} \fi

@@

\bigskip
\begin{abstract}
We consider the problem of supervised tensor decomposition with exponential-family entries given side information on multiple modes. Such data problems arise frequently in applications such as neuroimaging, network analysis, and spatial-temporal modeling. We propose a new family of tensor response regression that treats side-information as incorporate covariates and we establish the accuracy guarantees for our proposed estimation. Unlike earlier methods on unsupervised tensor decomposition, our estimation allows high-dimensionality in both the tensor data and the covariate matrix data on multiple modes. An efficient alternating updating algorithm is further developed. Our proposal handles a broad range of data types, including continuous, count, and binary observations. Through simulation and applications to two real datasets, we demonstrate the outperformance of our approach over the state-of-art.
\end{abstract}
